\section {Forester fonctionnalities}

	\subsection{Type primitif}

The manage of primitif type in Forester is not implemented yet. If you use pointer on primitif type, Forester returns this error :

\begin{lstlisting}
	int * integer = malloc(sizeof(int));
\end{lstlisting}
\bigskip

Forester return this resultat:
\begin{lstlisting}
error: BoxMan::getTypeInfo(): type for int not found!
\end{lstlisting}
\bigskip


The reason is primitif types have different representation in GCC and so Forester cans not recognize it. This fonctionnality is comming soon.
\\

But presentely, you can get around this problem with this solution :
\begin{lstlisting}
	struct T { int n; }* p_int;
	p_int = malloc(sizeof(*p_int));
	p_int->n = 10;
	free(p_int);
\end{lstlisting}
\bigskip

	\subsection{To use no allocated structure}
	
Before using dynamic structure, it needs to be allocated in memory. Forester checks if all dynamic stuctures are correctely allocated before they can be used. This example shows dynamic stucture which are used without allocation:
\begin{lstlisting}
	struct T { int n; }* pmi;
	pmi->n = 10;
\end{lstlisting}
\bigskip

In this case, Forester return this error:
\begin{lstlisting}
unallocated\_structure.c:7:9: note: #2317:pmi->n = (int)10
unallocated\_structure.c:7:9: error: dereferenced value is not a valid 
	reference [(undef)]
\end{lstlisting}
\bigskip

	\subsection{Dynamic structure not desallocated}
	
Forester cans check when a dynamic structure, who is correctely allocated, is not desallocated. In this example, pmi is allocated but this structure is not desallocated and the reference is lost after function's end :

\begin{lstlisting}
	struct T { int n; }* pmi;
	pmi = malloc(sizeof(*pmi));
	pmi->n = 10;
	return;
\end{lstlisting}
\bigskip

In this case, Forester returns this error:

\begin{lstlisting}
error: garbage detected
\end{lstlisting}
\bigskip

	\subsection{Reference to dynamic structure no catch in return of function}
	
Sometime, a function allocates a dynamic structure and returns the reference. In this case, it is important to catch this reference in the aim of desallocating this dynamic structure. Forester checks if all references returned by function are correctely caught.

\begin{lstlisting}
	struct T { int n; };
	typedef struct T T;

	T * foe()
	{
		return malloc(sizeof(T));
	}

	int main()
	{
		foe();
		return 0;
	}
\end{lstlisting}
\bigskip

In this case, Forester returns this error:

\begin{lstlisting}
error: assertion failed
\end{lstlisting}
\bigskip

This fonctionnality is user-friendly to avoid memory leaks. But it is possible function returns one reference to structure which are not allocated in this function. Forester returns the same error when this return is not caught.

\begin{lstlisting}
	struct T { int n; };
	typedef struct T T;

	T * foe(T * t)
	{
		return t;
	}

	int main()
	{
		T t;
		foe(&t);
		return 0;
	}
\end{lstlisting}
\bigskip